**Covid-19 vaccination in the province of Ontario: A geographical and socio-economical analysis**

### 2023-02-14 manuscript/04-discussion.qmd
working on discussion

Among the different challenges faced by Covid-19 vaccination efforts are the development of new variants due to inadequate public health measures [@li2021] and vaccine inequity  between low and high income countries[@tamey2022]. However, it is also well established that even in the case of high income countries that have had ample access to vaccines since 2020, such as the US, the UK, and Canada, there have been challenges in vaccination efforts due to differences in vaccine uptake among different segments of the population. More specifically, lower vaccine uptake has been associated with socio-economic factors such as race (i.e., identifying as Black, Asian, Indigenous) and household income (typically within lower income brackets) [@willis2021;@skirrow2022;@stoler2021;@khubchandani2021]. Reasons given for this association have included medical mistrust due to systemic medical racism, mistrust in vaccines, and the influence of conspiracy theories [@stoler2021;@willis2021;@bogart2021;@mosby2021;@freeman2020].

>>>>

Among the different challenges faced by Covid-19 vaccination efforts are the development of new variants due to inadequate public health measures [@li2021] and inequity in vaccine access between low and high income countries [@tamey2022]. However, it is also well established that even in the case of high income countries that have had ample access to vaccines since 2020, such as the US, the UK, and Canada, there have been challenges in vaccination efforts due to differences in vaccine uptake among different segments of the population. More specifically, lower vaccine uptake has been associated with socio-economic factors such as race (i.e., identifying as Black, Asian, Indigenous) and household income (typically within lower income brackets) [@willis2021;@skirrow2022;@stoler2021;@khubchandani2021]. Reasons given for this association have included medical mistrust due to systemic medical racism, mistrust in vaccines, and the influence of conspiracy theories [@stoler2021;@willis2021;@bogart2021;@mosby2021;@freeman2020].

In addition, vaccine uptake is influenced by geography as shown by different studies that have identified intra-regional differences in vaccine uptake [@pallathadka2022;@huang2022;@mollalo2021]. However, the majority of studies that have analyzed spatial differences in vaccination have been carried outside of Canada, where spatial analyses have been focused at the country level [@lavoie2022].

In this regard, we explored spatial and socio-economic determinants of vaccination status in the province of Ontario. This province is of particular interest as it has seen recently major structural health changes with the dissolution of the Local Health Integrated Networks (LHINs) and their incorporation into larger Health Regions [@dong2022]. The idea behind the change was to address the inequalities that were identified under the LHIN approach [@tsasis2012], and in the case of Covid-19 vaccination.

Our results indicate that across the most densely populated Health Regions of Ontario, almost three quarters of the surveyed individuals reported having received the first dose of a Covid-19 vaccine (@tbl-descriptive-stats). However, the likelihood of vaccination significant differed between age, race, and income (@tbl-model). These results are consistent with other studies that have shown significant lower vaccination in individuals within low income brackets [citations here]. In our case, individuals with a household income below CAD 39,999 were around 60% less likely of having received the vaccine when compared to individuals in high income households (with an income above 90,000 CAD).

### 2023-02-14 manuscript/main.qmd
Working on Discussion
working on discussion

---
title: '**Socio-economic and geographic determinants of Covid-19 vaccination**'
author: Ariel Mundo Ortiz
format: pdf
bibliography: refs.bib
csl: jama.csl
link-citations: yes #adds links to the citations
---

@@

>>>>

---
title: '**Covid-19 vaccination in the province of Ontario: A geographical and socio-economical analysis**'
author: Ariel Mundo Ortiz
format: pdf
linestretch: 2
bibliography: refs.bib
csl: jama.csl
link-citations: yes #adds links to the citations
---

@@

```{r}
#| child: 04-discussion.qmd
```
